Deep Convolutional networks for large scale image classification - A Survey

### 2015-01-25 paper/main.tex
finished draft1

% Title.
% ------
\title { Deep convolution networks for large scale image classification - A Survey  }
%
% Single address.
% ---------------
\name{Author(s) Name(s)\thanks{Thanks to XYZ agency for funding.}}
\address{Author Affiliation(s)}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%	{School A-B\\
%	Department A-B\\
%	Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%	while at ...}}
%	{School C-D\\
%	Department C-D\\
%	Address C-D}
%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
This paper explores the existing learning methods  in the area of image classification.
\end{abstract}
%
\begin{keywords}
One, two, three, four, five
\end{keywords}
%
\section{Introduction}
\label{sec:intro}
The performance of an  image  classification system mainly depends on the  extraction and  representation of features.  Feature representation methods like Haralick texture features \cite{Haralick1973} got attention from the research community from the earlier days of  image classification. However, to develop features that are invariant to position, rotation, sailing, distortion and  illumination changes motivated researchers to  explore the visual perception of primates. This research  leads to  the development of many models such as convolutional neural networks\cite{LeCun1998} and  Kohonen map\cite{kohonen1982self}. 
As a result, many successful image classification systems are  implemented with better accuracy \cite{lecun-89e}.

Early in that stage, method like the convolution network is limited by the  availability of labeled  data and computing infrastructure.  However, in the recent years, the development of  High performance computing architecture such as general purpose graphical processing units (GPGPU )  accelerated the research in this field. Large scale image  dataset such as ImageNet\cite{imagenet}  with  millions of labeled samples is also accessible to the research community. This changes in data and computing, put back the convolution network with million of parameters in track.

@@

\par Hubel DH and Wiesel TN \cite{Hubel1965a} presented a functional hierarchical structure of the visual cortex. According to their model, visual perception cells are in the  order, simple$\Longrightarrow$ complex$\Longrightarrow$ lower order hypercomplex $\Longrightarrow$ higher  order hypercomplex. Activation of  a lower stage is  influenced by  the position of the input patterns, and  higher stages are  position-invariant. There are several  contradictory to this structure, but no one   completely deny this hierarchical model.
\par Inspired by this work, Fukushima, K \cite{Stark1980} proposed a neural network model for pattern recognition called neocognitron.
In neocognitron , cells are arranged in  a number of  cascaded structure. Each  structure $U$ include a  simple cell layer $U_s$ and a complex cell layer $U_c$. This network is not affected by change in position or small distortion in the shape of patterns.  It is also capable of doing self-organization based on an unsupervised competitive learning algorithm\cite{Fukushima1982} in the first two layers and classification based on  supervised learning in the output layer.
\begin{figure}[ht]
 \includegraphics[]{Figures/neocognitron.eps}
\caption{Neocognitron\cite{Stark1980}}
\label{neo}
\end{figure}
\section{Convolutional Networks}
\par Neocognitron was improved by  Yann LeCun \cite{lecun-86},\cite{lecun-89d}, \cite{lecun-89e},\cite{lecun-90c}, \cite{lecun-90e} using backpropagation algorithm\cite{BRYSON1963} to train the entire system.
It uses  local receptive fields, share weights and  sub-sampling to achieve  shift, position and distortion invariance. A typical Convolutional Network called  LeNet-5 was proposed by   Yann LeCun et al..\cite{LeCun1998}  for document recognition. Using local receptive fields network can extract elementary visual features such as edges, end point, and corners. This features will combine to obtain high order features in the following layers.  Elementary feature detectors with identical weights can be useful in different parts of the image. So the units with  the same set of weights are arranged in plane and output from  the units of a plane is called  a feature map. Units in  a feature map perform the same operation on different parts of the same image. A convolution layer is composed of the set of feature maps with differently weighed units. In the implementation, a unit in the feature map scans the image and store the states in the feature map. This operation is equivalent to convolution with a kernel composed of a  set of weights and image.

\par
A typical convolutional  network composed of multiple stages with a filter bank layer, a non-linearity layer and a feature pooling layer \cite{lecun2010convolutional} followed by a classification network.\\
\emph{Filter Bank Layer:} This layer computes $y_{j}$ the convolution between a input feature map   $x_i$ and trainable filter kernel $k_{ij}$ 
. ie. $y_j=b_j+\sum_i {k_{ij}*x_i}$. Where $b_j$ is a trainable bias , $i$ and $j$ are  array indices.\\
\emph{Non-Linearity Layer:} This layer applies a non-linearity function such as $tanh(x)$ or $(1+e^{-x})^{-1}$ to unit output. But to reduce training time with gradient decent, new implementations uses the function $max(0,x)$. Units with this non-linearity is called Rectified Linear Units (ReLUs)\cite{Nair2010}.\\
\emph{Feature Pooling Layer:} It  reduces the dimension of  feature map by applying the techniques like averaging or max-pooling.

\section {Deep convolutional networks}
In last few years convolutional networks shows a significant performance improvement in many small scale image classification on data sets  such as MNIST\cite{Ciresan:2012g},CIFAR-10,CIFAR-100,SVHN\cite{lee2014deeply},STL-10 \cite{deepfwd}. One of the state-of-the-art error rate is from Krizhevsky, et al.\cite{Krizhevsky2012a}. Their network has 60 million parameters and 650,000 neurons, consists of five convolutional layers followed by max-pooling layers, and three fully-connected layers. Data set used in this experiment was subset of ImageNet dataset, used in the competition ImageNet Large-Scale Visual Recognition Challenge (ILSVRC)\cite{imagenet}. This data set includes 1.2 million images that contain 1,000 categories.

@@

@@

\section{Network In Network }
Inspired by the work of Ian J. Goodfellow et al..\cite{Goodfellow2013} on max out networks,  Min Lin et al. \cite{Lin2013} introduced a micro-network in each convolution layer so that it will compute more abstract features.This network gave a state-of-the-art performance in  ILSVRC 2013 competition with an error rate of 12.95\%.They used NVIDIA TITAN GPU to train the network.

\section{Visualizing and Understanding Convolutional Networks}

Matthew D. Zeiler and Rob Fergus\cite{Zeiler2013} presented a method to visualize the function of intermediate feature layers of CNNs and used as a diagnostic tool to improve  the model proposed by Krizhevsky et al. \cite{Krizhevsky2012a}. This method helped  them  to understand  the activation in the feature maps with respect to the input patterns. It shows Krizhevsky et al..'s architecture does not have  enough mid frequency coverage in the first layer filters and aliasing artifacts caused by  large stride in the first layer convolutions. Authors solved this problems by decreasing filter size to $7\times7$ and reducing stride to 2.This implementation won the  ILSVRC 2013 competition with an error rate of 11.74\%

@@

\section{Spatial pyramid pooling in Deep Convolutional Networks}
Instead of using fixed input size in CNNs, Kaiming He et al. \cite{He2014} suggested  the use of a spooling strategy called  spatial pyramid pooling(SPP)\cite{Grauman2005}\cite{1641019} to avoid cropping or warping of  images. It introduced a new layer on top of the convolution layer and perform aggregation  based on Bag-of-Words (BoW) model \cite{Sivic2003}. However, the classical backpropagation training methods expect layers to have a fixed   size. To overcome this problem author implemented two fixed size networks with shared parameters and switched the network on alternate epochs. This network is trained using a single GeForce GTX Titan GPU with a starting  learning rate of 0.01 and achieved  a less  error rate of 8.06\% on  ILSVRC 2014 data set. 
\par 
This implementation improves the performance of baseline architectures including ZF-5\cite{Zeiler2013} , Convnet \cite{Krizhevsky2012a} and Overfeat-5/7 \cite{Sermanet2013}. Their study shows; accuracy of CNNs will improve on multi-size training, multi-level pooling, and full-image representations. 
%

\section{Going deeper with convolutions }
Christian Szegedy and et al. \cite{Szegedy} proposed a network named GoogLeNet with receptive field(input layer) of size $244\times244$ with the number of layers around 100. Network is trained using asynchronous stochastic gradient descent with 0.9 momentum and fixed learning rate schedule based on  no of epochs 
. Learning procedure took advantage of  model and data-parallelism in a CPU-based cluster environment. This network gave an error rate of  6.67\%  on  ILSVRC 2014 data set. Their result shows that use of existing dense  blocks to  build the sparse structure can improve the  performance of convolutional networks.

\section{VERY DEEP CONVOLUTIONAL NETWORKS FOR LARGE-SCALE IMAGE RECOGNITION}
Karen Simonyan and Andrew Zisserman \cite{Arge2015} evaluated the effect of network depth in image classification using very small convolution filters. Their deep network architecture comprise of fixed  size input layers , a stack of convolution layers , three Fully-Connected (FC) layers and  5 max-pooling layers for spatial spooling  over a $2 \times 2$ pixel window with stride 2. Hidden layers are modeled using Rectified Linear Units(ReLU)\cite{Nair2010}. On the hardware side, it uses a multi-GPU system with NVIDIA Titan Black GPUs. Network is trained using multinomial logistic regression  based on backpropagation with momentum of 0.9 and  batch size  256.
\par
 In this work authors formed a conclusion that greater depth with small convolution filters and  initialization of certain layers will cause the learning process to converge in less number  of epochs. This model of the convolution network does not differ from the classical architecture proposed by  LeCun et  al. \cite{LeCun1998}. But the authors reported a significant improvement in the performance using an increased depth.  This implementation results in a significant improvement in accuracy with  an error rate of  6.8\% in  ILSVRC 2014 of ImageNet.

\begin{section}{Deep Image: Scaling up Image Recognition}
The latest attempt in image classification with an error 5.98\% in ImageNet data set is reported by  Ren Wu et al. \cite{Wu2015} of Baidu research.They developed an end to end deep learning  system named Deep Image. It uses a highly optimized parallel algorithm  to implement large deep neural network with augmented input data. The network is trained using stochastic gradient decent algorithms (SGD)[ref] on a custom built high performance system comprised of 36 server nodes, each with 2 six-core Intel Xeon E5-2620 processors and 4 NVIDIA Tesla K40m GPUs . System  uses an InfiniBand  network for interconnections. Parallelism strategies used in their network are model-data parallelism and data parallelism.  These methods have been proposed by Alex Krizhevsky \cite{Krizhevsky2014} and Omry Yadan et al. \cite{Yadan2013} for training convolutional neural networks with SGD on a  multiple GPU systems. However, it is not easy extend the same strategies to multiple GPU clusters because of the communication overhead. So the  Baidu Team focused on minimizing network data transfers and overlapping the computation. They use butterfly synchronization and lazy update strategies to achieve data parallelism in the gradient computation. Their results show model-data parallelism is better when number of GPUs is less than 16. Implementation of Data parallelism in a large number  of GPU  cluster is better because of the constant communication requirements.
\par
The authors have explored different data augmentation techniques to increase the number of labeled images in the training set. This includes color casting, Vignetting, Lens distortion, Rotation, Flipping, and  Cropping. Instead of using the same resolution on all images, they have trained separate models at different scales, combined results by averaging soft-max class posteriors.

\par
 Major contribution of this work is the demonstration of tremendous computational power to achieve high accuracy in image classification.
It also shows augmented multi-scale images can be combined to achieve less error rate in convolutional network in the context of the image classification. 
 \end{section}

>>>>

% Title.
% ------
\title { Deep Convolutional networks for large scale image classification - A Survey  }
%
% Single address.
% ---------------
\name{Author(s) Name(s)}
\address{Author Affiliation(s)}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%	{School A-B\\
%	Department A-B\\
%	Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%	while at ...}}
%	{School C-D\\
%	Department C-D\\
%	Address C-D}
%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
Image classification is an essential to the field of computer vision  based systems and recent research in this area explores better feature extraction, feature coding, and classification.  The purpose of this paper is to review the application of supervised  deep convolution networks in this field.   Numerous techniques have been reported to improve the performance of the convolution networks.   It has been shown that with a large amount of labeled data, convolution networks can learn very complex functions such as image classification and speech recognition.

\end{abstract}
%
\begin{keywords}
convolution networks, deep learning , neural networks.
\end{keywords}
%
\section{Introduction}
\label{sec:intro}
The performance of an  image  classification system mainly depends on the  extraction and  representation of features.  Feature representation methods like Haralick texture features \cite{Haralick1973} got attention from the research community from the earlier days of  image classification. However, to develop features that are invariant to position, rotation, sailing, and distortion, researchers had  to  explore the visual perception of primates. This research  leads to  the development of many models such as convolutional neural networks\cite{LeCun1998} and  Kohonen map\cite{kohonen1982self}. 
As a result, many successful image classification systems are  implemented with better accuracy \cite{lecun-89e}.

Early in that stage, method like the convolutional network is limited by the  availability of labeled  data and computing infrastructure.  However, in the recent years, the development of  High performance computing architecture such as general purpose graphical processing units (GPGPU )  accelerated the research in this field. Large scale image  dataset such as ImageNet\cite{imagenet}  with  millions of labeled samples is also accessible to the research community. This changes in data and computing, put back the convolution network with million of parameters in track.

@@

\par Hubel DH and Wiesel TN \cite{Hubel1965a} presented a functional hierarchical structure of the visual cortex. According to their model, visual perception cells are in the  order, simple$\Longrightarrow$ complex$\Longrightarrow$ lower order hypercomplex $\Longrightarrow$ higher  order hypercomplex. Activation of  a lower stage is  influenced by  the position of the input patterns, and  higher stages are  position-invariant. There are several  contradictory to this structure, but no one   completely deny this hierarchical model.
\par Inspired by this work, Fukushima, K \cite{Stark1980} proposed a neural network model for pattern recognition called neocognitron.
In neocognitron , cells are arranged in  a number of  cascaded structure. Each  structure $U$ include a  simple cell layer $U_s$ and a complex cell layer $U_c$. This network is not affected by change in position or small distortion in the shape of patterns.  It is also capable of doing self-organization based on an unsupervised competitive learning algorithm\cite{Fukushima1982} in the first two layers and classification based on  supervised learning in the output layer.
\begin{figure}[ht]
 \centering
 \includegraphics[width=9cm]{Figures/neocognitron.eps}
\caption{Neocognitron\cite{Stark1980}}
\label{neo}
\end{figure}
\section{Convolutional Networks}
\par Neocognitron was improved by  Yann LeCun \cite{lecun-86},\cite{lecun-89d}, \cite{lecun-89e},\cite{lecun-90c}, \cite{lecun-90e} using backpropagation algorithm\cite{BRYSON1963} to train the entire system.
It uses  local receptive fields, share weights and  sub-sampling to achieve  shift, position and distortion invariance. A typical Convolutional Network called  LeNet-5 was proposed by   Yann LeCun et al..\cite{LeCun1998}  for document recognition. Using local receptive fields network can extract elementary visual features such as edges, end point, and corners. This features will combine to obtain high order features in the following layers.  Elementary feature detectors with identical weights can be useful in different parts of the image. So the units with  the same set of weights are arranged in plane and output from  the units of a plane is called  a feature map. Units in  a feature map perform the same operation on different parts of the same image. A convolution layer is composed of the set of feature maps with differently weighed units. In the implementation, a unit in the feature map scans the image and store the states in the feature map. This operation is equivalent to convolution with a kernel composed of a  set of weights and image.

\par
A typical convolutional  network composed of multiple stages with a filter bank layer, a non-linearity layer and a feature pooling layer \cite{lecun2010convolutional} followed by a classification network.\\
\begin{figure}[ht]
 \includegraphics[width=9.5cm]{Figures/convent.eps}
\caption{A typical ConvNet architecture \cite{lecun2010convolutional}}
\label{net}
\end{figure}
\emph{Filter Bank Layer:} This layer computes $y_{j}$ the convolution between a input feature map   $x_i$ and trainable filter kernel $k_{ij}$ 
. ie. $y_j=b_j+\sum_i {k_{ij}*x_i}$. Where $b_j$ is a trainable bias , $i$ and $j$ are  array indices.\\
\emph{Non-Linearity Layer:} This layer applies a non-linearity function such as $tanh(x)$ or $(1+e^{-x})^{-1}$ to unit output. But to reduce training time with gradient decent, new implementations uses the function $max(0,x)$. Units with this non-linearity is called Rectified Linear Units (ReLUs)\cite{Nair2010}.\\
\emph{Feature Pooling Layer:} It  reduces the dimension of  feature map by applying the techniques like averaging or max-pooling.
\begin{figure}[ht]
 \centering
 \includegraphics[width=8cm]{Figures/conv.eps}
\caption{Output of  a randomly initialized   convolution filter. Input image courtesy:dcsku.org}
\label{conv}
\end{figure}

@@

\section {Deep convolutional networks}
In last few years convolutional networks shows a significant performance improvement in many small scale image classification on data sets  such as MNIST\cite{Ciresan:2012g},CIFAR-10,CIFAR-100,SVHN\cite{lee2014deeply},STL-10 \cite{deepfwd}. One of the state-of-the-art error rate is from Krizhevsky, et al.\cite{Krizhevsky2012a}. Their network has 60 million parameters and 650,000 neurons, consists of five convolutional layers followed by max-pooling layers, and three fully-connected layers. Data set used in this experiment was a subset of ImageNet dataset, used in the competition ImageNet Large-Scale Visual Recognition Challenge (ILSVRC)\cite{imagenet} and reported an error rate of 15.3\%. This data set includes 1.2 million images that contain 1,000 categories.

@@

\subsection{Network In Network }
Inspired by the work of Ian J. Goodfellow et al..\cite{Goodfellow2013} on max out networks,  Min Lin et al. \cite{Lin2013} introduced a micro-network in each convolution layer so that it will compute more abstract features.This network gave a state-of-the-art performance in  ILSVRC 2013 competition with an error rate of 12.95\%.They used NVIDIA TITAN GPU to train the network.

\subsection{Visualizing Convolutional Networks}

Matthew D. Zeiler and Rob Fergus\cite{Zeiler2013} presented a method to visualize the function of intermediate feature layers of convolutional networks and used as a diagnostic tool to improve  the model proposed by Krizhevsky et al. \cite{Krizhevsky2012a}. This method helped  them  to understand  the activation in the feature maps with respect to the input patterns. It shows Krizhevsky et al..'s architecture does not have  enough mid frequency coverage in the first layer filters and aliasing artifacts caused by  large stride in the first layer convolutions. Authors solved this problems by decreasing filter size to $7\times7$ and reducing stride to 2.This implementation won the  ILSVRC 2013 competition with an error rate of 11.74\%.

@@

\subsection{Spatial pyramid pooling in Deep Convolutional Networks}
Instead of using fixed input size in convolutional networks, Kaiming He et al. \cite{He2014} suggested  the use of a spooling strategy called  spatial pyramid pooling(SPP)\cite{Grauman2005}\cite{1641019} to avoid cropping or warping of  images. It introduced a new layer on top of the convolution layer and perform aggregation  based on Bag-of-Words (BoW) model \cite{Sivic2003}. However, the classical backpropagation training methods expect layers to have a fixed   size. To overcome this problem author implemented two fixed size networks with shared parameters and switched the network on alternate epochs. This network is trained using a single GeForce GTX Titan GPU with a starting  learning rate of 0.01 and achieved  a less  error rate of 8.06\% on  ILSVRC 2014 data set. 
\par 
This implementation improves the performance of baseline architectures including ZF-5\cite{Zeiler2013} , Convnet \cite{Krizhevsky2012a} and Overfeat-5/7 \cite{Sermanet2013}. Their study shows; accuracy of convolutional networks will improve on multi-size training, multi-level pooling, and full-image representations. 
%

\subsection{Going deeper with convolutions }
Christian Szegedy and et al. \cite{Szegedy} proposed a network named GoogLeNet with receptive field(input layer) of size $244\times244$ with the number of layers around 100. Network is trained using asynchronous stochastic gradient descent with 0.9 momentum and fixed learning rate schedule based on  no of epochs 
. Learning procedure took advantage of  model and data-parallelism in a CPU-based cluster environment. This network gave an error rate of  6.67\%  on  ILSVRC 2014 data set. Their result shows that use of existing dense  blocks to  build the sparse structure can improve the  performance of convolutional networks.

\section{VERY DEEP CONVOLUTIONAL NETWORKS }
Karen Simonyan and Andrew Zisserman \cite{Arge2015} evaluated the effect of network depth in image classification using very small convolution filters. Their deep network architecture comprise of fixed  size input layers , a stack of convolution layers , three Fully-Connected (FC) layers and  5 max-pooling layers for spatial spooling  over a $2 \times 2$ pixel window with stride 2. Hidden layers are modeled using Rectified Linear Units(ReLU)\cite{Nair2010}. On the hardware side, it uses a multi-GPU system with NVIDIA Titan Black GPUs. Network is trained using multinomial logistic regression  based on backpropagation with momentum of 0.9 and  batch size  256.
\par
 In this work authors formed a conclusion that greater depth with small convolution filters and  initialization of certain layers will cause the learning process to converge in less number  of epochs. This model of the convolution network does not differ from the classical architecture proposed by  LeCun et  al. \cite{LeCun1998}. But the authors reported a significant improvement in the performance using an increased depth.  This implementation results in a significant improvement in accuracy with  an error rate of  6.8\% in  ILSVRC 2014 of ImageNet.

\begin{subsection}{Scaling up Image Classification}
The latest attempt in image classification with an error 5.98\% in ImageNet data set is reported by  Ren Wu et al. \cite{Wu2015} of Baidu research.They developed an end to end deep learning  system named Deep Image. It uses a highly optimized parallel algorithm  to implement large deep neural network with augmented input data. The network is trained using stochastic gradient decent algorithms (SGD on a custom built high performance system comprised of 36 server nodes, each with 2 six-core Intel Xeon E5-2620 processors and 4 NVIDIA Tesla K40m GPUs . System  uses an InfiniBand  network for interconnections. Parallelism strategies used in their network are model-data parallelism and data parallelism.  These methods have been proposed by Alex Krizhevsky \cite{Krizhevsky2014} and Omry Yadan et al. \cite{Yadan2013} for training convolutional neural networks with SGD on a  multiple GPU systems. However, it is not easy extend the same strategies to multiple GPU clusters because of the communication overhead. So the  Baidu Team focused on minimizing network data transfers and overlapping the computation. They use butterfly synchronization and lazy update strategies to achieve data parallelism in the gradient computation. Their results show model-data parallelism is better when number of GPUs is less than 16. Implementation of Data parallelism in a large number  of GPU  cluster is better because of the constant communication requirements.
\par
The authors have explored different data augmentation techniques to increase the number of labeled images in the training set. This includes color casting, Vignetting, Lens distortion, Rotation, Flipping, and  Cropping. Instead of using the same resolution on all images, they have trained separate models at different scales, combined results by averaging soft-max class posteriors.

\par
 Major contribution of this work is the demonstration of tremendous computational power to achieve high accuracy in image classification.
It also shows augmented multi-scale images can be combined to achieve less error rate in convolutional network in the context of the image classification. 
 \end{subsection}
 \section {Summary}
 \begin{enumerate}

 \item Wisely chosen data  augmentation techniques can increase the performance of the network.
 \item Data parallelism and model parallelism can increase the speed of the training process.
 \item Greater depth with small convolution filters will improve the accuracy.
 \item Network will get benefited from   image  in different scale .
 \item Use of different pooling technique such as spatial pyramid pooling in sub-architectural  level may reduce the error rate. 
 \item  Rectified Linear Units can increase the speed of SGD.

 \end{enumerate}

 \begin{table}[h]
 \begin{tabular}{ | p{5cm} | l | l |}
    \hline
Team	&Year	&Top 5 error\\
    \hline
        \hline
Ren Wu et al.\cite{Wu2015}	&2015	&5.98\%\\
    \hline
Karen Simonyan and Andrew Zisserman.\cite{Arge2015}	&2014	&6.80\%\\
    \hline
Christian Szegedy and et al.\cite{Szegedy}	&2014	&6.67\%\\
    \hline
Kaiming He et al.\cite{He2014}	&2014	&8.06\%\\
    \hline
Matthew D. Zeiler and Rob Fergus \cite{Zeiler2013}	&2013	&11.74\%\\
    \hline
Min Lin et al.\cite{Lin2013}	&2013	&12.95\%\\
    \hline
Krizhevsky, et al.\cite{Krizhevsky2012a}	&2012	&15.30\%\\
    \hline

\end{tabular}
\caption[]{ Top 5 error rate in ILSVRC}
\end{table}

\section{conclusion}
This paper attempts to provide a  review of research on deep convolutional networks  and provide an overview of  its architecture and performance. Majority of the reviewed  works are reported from ImageNet Largqe-Scale Visual Recognition Challenge. There is no work exist to our knowledge, that explain all underpinning mathematics  of  deep convolutional  networks. This networks can only be trained using very expensive computing resources such as multiGPU cluster  to achieve more accuracy on large data sets. So  this research heavily depends on other research domains such as parallel algorithms, computer networks and multicore architecture. Because of the heavy computational requirements, it is not easy to apply this method directly  to the small level computing platforms such as embedded systems and application level  processors. On the other side, this methods can easily bring  live with the help of  cloud computing infrastructure, so to the mobility solutions such as mobile phones and the web.
